---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading R library
```{r}
library("dplyr")
library("ggplot2")

```

## Loading and preprocessing the data
```{r readProcData, echo = TRUE}
tPath <- "D:/00-PDrive/MyStudy/01-Course/00-Coursera/2-DSFusingR/5-Reproducible/Project1"
setwd(tPath)
master <- as.character(unzip("repdata_data_activity.zip", list = TRUE)$Name)
Dat <- read.csv(unz("repdata_data_activity.zip", "activity.csv"), header = TRUE, sep = ",") 
dim(Dat)
head(Dat)
Dat$date <- as.Date(Dat$date, "%Y-%m-%d")
str(Dat)

```
## What is mean total number of steps taken per day?

- Aggregation total steps according to day
```{r totStep, echo = TRUE}
totSteps <- Dat %>%
    group_by(date) %>%
    summarise_at(vars(steps), list(totSteps = sum), na.rm = TRUE)
totStepsbyDay <- as.data.frame(totSteps)
head(totStepsbyDay)

```
- Draw a graph to show the total number of steps for each day
```{r totGraph, echo = TRUE, fig.width = 8}
g <- ggplot(data = totStepsbyDay, aes(x= date, y = totSteps))
g <- g + geom_bar(stat = "identity", color="blue", fill="steelblue")
g + ylab("Total Steps") + xlab("") 

```

- Histogram of the total number of steps taken each day
```{r echo = TRUE, fig.width = 8}
hist(totStepsbyDay$totSteps, xlab = "Total Steps per Dat", main = "Histogram of the total number of steps taken each day")

```

- Mean and median of the total number of steps taken per day:  `r as.integer(mean(totStepsbyDay$totSteps))` and `r as.integer(median(totStepsbyDay$totSteps))`

```{r meanMD, echo = TRUE}
summary(totStepsbyDay$totSteps)

```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
