---
title: 'Reproducible Research: Peer Assessment 1'
output:
  html_document:
    keep_md: yes
  pdf_document: default
---

## Loading R library
```{r}
library("dplyr")
library("ggplot2")
library("Hmisc")
library("timeDate")

```

## Loading and preprocessing the data
```{r readProcData, echo = TRUE}
tPath <- "D:/00-PDrive/MyStudy/01-Course/00-Coursera/2-DSFusingR/5-Reproducible/Project1"
setwd(tPath)
master <- as.character(unzip("repdata_data_activity.zip", list = TRUE)$Name)
Dat <- read.csv(unz("repdata_data_activity.zip", "activity.csv"), header = TRUE, sep = ",") 
dim(Dat)
head(Dat)
Dat$date <- as.Date(Dat$date, "%Y-%m-%d")
str(Dat)

```
## What is mean total number of steps taken per day?

- Aggregation total steps according to day
```{r totStep, echo = TRUE}
totSteps <- Dat %>%
    group_by(date) %>%
    summarise_at(vars(steps), list(totSteps = sum), na.rm = TRUE)
totStepsbyDay <- as.data.frame(totSteps)
head(totStepsbyDay)

```
- Draw a graph to show the total number of steps for each day
```{r totGraph, echo = TRUE, fig.width = 8}
g <- ggplot(data = totStepsbyDay, aes(x= date, y = totSteps))
g <- g + geom_bar(stat = "identity", color="blue", fill="steelblue")
g + ylab("Total Steps") + xlab("") 

```

- Histogram of the total number of steps taken each day
```{r echo = TRUE, fig.width = 8}
hist(totStepsbyDay$totSteps, xlab = "Total Steps per Dat", main = "Histogram of the total number of steps taken each day")

```

- Mean and median of the total number of steps taken per day:  `r as.integer(mean(totStepsbyDay$totSteps))` and `r as.integer(median(totStepsbyDay$totSteps))`

```{r meanMD, echo = TRUE}
summary(totStepsbyDay$totSteps)

```

## What is the average daily activity pattern?

- The time series plot of the average number of steps taken

```{r echo = TRUE, fig.width = 10}
mSteps <- Dat %>%
    group_by(interval) %>%
    summarise_at(vars(steps), list(meanSteps = mean), na.rm = TRUE)
meanSteps <- as.data.frame(mSteps)
head(meanSteps)
maxPos <- which.max(meanSteps$meanSteps)
maxIntv <- meanSteps[maxPos, 1]
with(meanSteps, plot(x = interval, y = meanSteps, type = "l", 
    xlab = "5-minute interval", ylab = "Average number of steps", 
    main = "Average daily activity pattern"))
abline(v = maxIntv, col = "red")

```

- The maximum 5-minute interval is at `r maxIntv` and the value is `r as.integer(meanSteps[maxPos, 2])`. 

## Imputing missing values

- impute steps with mean value using r "Hmisc" package

```{r echo = TRUE}
Dat$imputedSteps <- with(Dat, impute(steps, mean))
head(Dat)

```

- Aggregation total steps according to day using imputed data

```{r echo = TRUE}
totSteps_I <- Dat %>%
    group_by(date) %>%
    summarise_at(vars(imputedSteps), list(totSteps = sum), na.rm = TRUE)
totStepsbyDay_I <- as.data.frame(totSteps_I)
head(totStepsbyDay_I)

```

- Histogram of the total number of steps taken each day using imputed data

```{r echo = TRUE, fig.width = 8}
hist(totStepsbyDay_I$totSteps, xlab = "Total Steps per Dat", 
     main = "Histogram of the total number of steps taken each day using imputed data")
```

## Are there differences in activity patterns between weekdays and weekends?

- Add a logic weekend column

```{r echo = TRUE}
Dat$Weekend <- isWeekend(Dat$date, wday = 1:5)
head(Dat)

```

- Aggregate mean steps for both week day and week end

```{r echo = TRUE}
mSteps_wkDay <- Dat %>%
    filter(Weekend == FALSE) %>%
    group_by(interval) %>%
    summarise_at(vars(steps), list(meanSteps = mean), na.rm = TRUE)
meanSteps_wkDay <- as.data.frame(mSteps_wkDay)
head(meanSteps_wkDay)
mSteps_wkEnd <- Dat %>%
    filter(Weekend == TRUE) %>%
    group_by(interval) %>%
    summarise_at(vars(steps), list(meanSteps = mean), na.rm = TRUE)
meanSteps_wkEnd <- as.data.frame(mSteps_wkEnd)
head(meanSteps_wkEnd)

```

- Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r echo = TRUE, fig.width = 10}
rng <- range(meanSteps_wkDay$meanSteps, meanSteps_wkEnd$meanSteps)
par(mfrow = c(1, 2))
with(meanSteps_wkDay, plot(x = interval, y = meanSteps, type = "l", ylim = rng, 
                           xlab = "5-minute interval", ylab = "Average number of steps", 
                           main = "Average daily activity pattern in week day"))
with(meanSteps_wkEnd, plot(x = interval, y = meanSteps, type = "l", ylim = rng, 
                           xlab = "5-minute interval", ylab = "Average number of steps", 
                           main = "Average daily activity pattern in week end"))

```









